
\documentclass[a4paper,11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[margin=2mm]{geometry}
\usepackage{graphicx}
\usepackage{amsfonts}
\input{card_template.tex}
    
    \begin{document}
    
\card{red}{Flippers}{}{flippers}{Resource -- \textbf{Actuation}}{\textit{`The time has come,' the walrus said, `to talk of many things.''}}{}
\card{red}{Vacuum Gripper}{}{vacuum_gripper}{Resource -- \textbf{Actuation}}{\textit{Where the bee sucks, there suck I; In a cowslip's bell I lie.}}{}
\card{red}{Cyber-Cockroach}{}{cyber_cockroach}{Resource -- \textbf{Actuation}}{A biological cockroach with implants for computer control.\par\vfill\textit{Any foolish boy can stamp on a beetle, but all the professors in the world cannot make a beetle.}\par\vspace*{\fill}}{}



\card{red}{Weasel Ball}{}{weaselball}{Resource -- \textbf{Actuation}}{\textit{Methinks it is like a weasel.}}{}
\card{red}{Pheromones}{}{pheromones}{Resource -- \textbf{Actuation}}{An emitter of artificial pheromones.
\par\vfill\textit{How full and rich a world theirs to inhabit is---Sweet scent of grass and bloom.}\par\vspace*{\fill}}{}
\card{red}{Tesla Model X Chassis}{}{model_x_chassis}{Resource -- \textbf{Actuation}}{\textit{Today's scientists \ldots{} wander off through equation after equation, and eventually build a structure which has no relation to reality.}}{}



\card{red}{Segway Base}{}{segway_base}{Resource -- \textbf{Actuation}}{\textit{Life is like riding a bicycle. To keep your balance, you must keep moving.}}{}
\card{red}{Speaker}{}{loudspeaker}{Resource -- \textbf{Actuation}}{\textit{A sound so fine, there's nothing lives twixt it and silence.}}{}
\card{red}{Differential Drive}{}{ddr}{Resource -- \textbf{Actuation}}{A platform with two independently-powered wheels.\par\vfill\textit{Change does not roll in on the wheels of inevitability, but comes through continuous struggle.}\par\vspace*{\fill}}{}


\clearpage
\card{red}{RGB LED}{}{led}{Resource -- \textbf{Actuation}}{\textit{The rainbow comes and goes, And lovely is the rose.}}{}
\card{red}{Christmas Lights}{}{christmas_lights}{Resource -- \textbf{Actuation}}{\textit{Not a creature was stirring, not even a mouse.}}{}
\card{red}{Tracks}{}{tracks}{Resource -- \textbf{Actuation}}{\textit{One woe doth tread upon another's heel.}}{}



\card{red}{RC Car Chassis}{}{rc_car_chassis}{Resource -- \textbf{Actuation}}{\textit{I would have nobody to control me; I would be absolute: and who but I?}}{}
\card{red}{Circular Saw}{}{circular_saw}{Resource -- \textbf{Actuation}}{\textit{I don't think so, Tim.}}{}
\card{red}{Legs}{}{2legs}{Resource -- \textbf{Actuation}}{A pair of humanoid legs.\par\vfill\textit{A traveller at Sparta, standing long upon one leg, said to a Laced\ae{}monian, `I do not believe you can do as much.' `True,' said he, `but every goose can.'}\par\vspace*{\fill}}{6359.90 USD}



\card{red}{Finger}{}{finger1}{Resource -- \textbf{Actuation}}{\textit{``When the finger points to the moon, the student looks at the finger.''}}{}
\card{red}{DC Motor}{}{dcmotor}{Resource -- \textbf{Actuation}}{\textit{Have power, will rotate!}}{}
\card{red}{Pair of Wheels}{}{wheels}{Resource -- \textbf{Actuation}}{\textit{The wheel is come full circle.}}{}


\clearpage
\card{red}{Hand}{}{1hand}{Resource -- \textbf{Actuation}}{\textit{With one hand he put a penny in the urn of poverty, and with the other took a shilling out.}}{}
\card{red}{Cheap Pan-Tilt Kit}{}{lynxmotion_pan_tilt_kit}{Resource -- \textbf{Actuation}}{A cheap pan-tilt kit made of two HiTec servos (HS-422) and two Lynxmotion servo brackets.\par\vfill\textit{Do you see over yonder, friend Sancho, thirty or forty hulking giants? I intend to do battle with them and slay them.}\par\vspace*{\fill}}{29 USD}
\card{red}{Bar Magnet}{}{magnetic_field}{Resource -- \textbf{Actuation}}{0.01 Tesla of pure magnetism.\par\vfill\textit{Are you a firm believer in miracles?}\par\vspace*{\fill}}{}



\card{red}{Linear Actuator}{}{linear_actuator}{Resource -- \textbf{Actuation}}{Creates motion in a straight line.\par\vfill\textit{Straight down the crooked lane, and all round the square.}\par\vspace*{\fill}}{}
\card{red}{High-Quality Pan-Tilt Kit}{}{servocity_pt2100_pan_tilt_kit}{Resource -- \textbf{Actuation}}{This professional pan-tilt kit can move a payload of up to 10 kg.\par\vfill\textit{`Take care, sir,' cried Sancho. `Those over there are not giants but windmills.'}\par\vspace*{\fill}}{8.5 lbs; 1,199.99 USD}
\card{red}{Balloon}{}{balloon}{Resource -- \textbf{Actuation}}{\textit{Would you like to ride in my beautiful balloon?}}{}



\card{red}{Tentacle}{}{1tentacle}{Resource -- \textbf{Actuation}}{\textit{Talent without discipline is like an octopus on roller skates.}}{}
\card{red}{Puppetry Wires}{}{puppetry_wires}{Resource -- \textbf{Actuation}}{\textit{I know what I look like---a weird, sad clown puppet. I'm fine with that.}}{}
\card{red}{Propellers}{}{2propellers}{Resource -- \textbf{Actuation}}{A pair of propellers.  They convert rotation to thrust.\par\vfill\textit{If the young person \ldots{} has poetry in him or her, to offer them help is like offering a propeller to a bird.}\par\vspace*{\fill}}{}


\clearpage
\card{red}{Steerable Needle}{}{steerable_needle}{Resource -- \textbf{Actuation}}{\textit{If you don't like what you're doing, you can always pick up your needle and move to another groove.}}{}
\card{brown}{300 Duckies in a Bag}{}{bag_of_duckies}{Resource -- \textbf{Materials}}{\textit{Anything to declare?}}{}
\card{brown}{Standard Duckie}{}{duckie}{Resource -- \textbf{Materials}}{}{}



\card{brown}{Giant Rubber Duckie}{}{giant_rubber_duckie}{Resource -- \textbf{Materials}}{}{}
\card{magenta}{Titan XIII}{}{titanXIII}{Resource -- \textbf{Platform}}{The newest sprawling-type quadruped robot from the Hirose/Fukushima laboratory at Tokyo Institute of Technology.
}{}
\card{magenta}{ACM-R5 Amphibious Snake}{}{ACMR5_snake}{Resource -- \textbf{Platform}}{Snake robot from the Hirose/Fukushima laboratory at Tokyo Institute of Technology.
\par\vfill\textit{Now the serpent was more subtle than any beast of the field\ldots}\par\vspace*{\fill}}{}



\card{magenta}{Baxter}{}{baxter}{Resource -- \textbf{Platform}}{A robot designed by RethinkRobotics.
}{25,000 USD}
\card{magenta}{Youbot}{}{kuka_youbot}{Resource -- \textbf{Platform}}{Omnidirectional mobile platform with 5 DOF arm, designed by KUKA.}{30,000 USD}
\card{magenta}{Gimball}{}{gimball}{Resource -- \textbf{Platform}}{A flying robot that can survive impacts with the environment, designed by Floreano (EPFL).
}{}


\clearpage
\card{magenta}{R2 Astromech Droid}{}{r2d2}{Resource -- \textbf{Platform}}{The popiular series of astromech droids manufactured by Industrial Automaton.
\par\vfill\textit{``An extremely well put-together little droid.''
}\par\vspace*{\fill}}{}
\card{magenta}{Robobee}{}{robobee}{Resource -- \textbf{Platform}}{A miniature robotic insect, designed by Wood (Harvard).
}{}
\card{magenta}{3D Hopper}{}{3D_hopper}{Resource -- \textbf{Platform}}{The 3D Hopper was created in 1988 by Marc Raibert while at MIT, before he left to found Boston Dynamics.
\par\vfill\textit{Good wits jump; a word to the wise is enough.}\par\vspace*{\fill}}{}



\card{magenta}{Dragon Runner}{}{dragon_runner}{Resource -- \textbf{Platform}}{A compact remote-controlled robot used by the British army, designed by CMU.
}{20 lbs; 120,000 USD}
\card{magenta}{PR2}{}{pr2}{Resource -- \textbf{Platform}}{The PR2 has two 7-DOF arms with a payload of 1.8 kilograms, and an omnidirectional base.}{280,000 USD}
\card{magenta}{DJI Phantom 4}{}{dji_phantom_4}{Resource -- \textbf{Platform}}{}{400 USD}



\card{magenta}{Duckiebot}{}{duckiebot}{Resource -- \textbf{Platform}}{A low-cost educational platform. 
}{}
\card{blue}{Military-Grade FOG}{}{astrix_1090}{Resource -- \textbf{Sensing}}{The Astrix 1090 is a 3-axis fiber-optic gyroscope produced by Airbus.  It is designed to work for >20 years in small satellites. 
}{12 W; 4.2 kg; 100,000 USD}
\card{blue}{GelSight}{}{gelsight}{Resource -- \textbf{Sensing}}{An image-based tactile sensor that works by sensing the deformation of a thin film in contact with the object.
}{}


\clearpage
\card{blue}{Kinect}{}{kinect}{Resource -- \textbf{Sensing}}{An RGB camera, depth sensor and multi-array microphone running proprietary software, which provide full-body 3D motion capture, facial recognition and voice recognition capabilities.}{99 USD}
\card{blue}{Parabolic Mirror}{}{parabolic_mirror}{Resource -- \textbf{Sensing}}{Turns a camera into an omnidirectional camera.}{}
\card{blue}{Artificial Ocelli Sensor}{}{ocelli}{Resource -- \textbf{Sensing}}{Four defocused photoreceptors that can provide enough information to estimate the platform attitude, designed by Fuller (Harvard/UW).
}{}



\card{blue}{Sick LMS511 Range Finder}{}{Sick_LMS511_11100_Lite}{Resource -- \textbf{Sensing}}{A 2D, 190 deg, range finder with 0.25 deg resolution per ray. The maximum range is 80m.}{22 W; 3.7 kg; 7000 USD}
\card{blue}{Olfactory Sensor}{}{odour_sensor}{Resource -- \textbf{Sensing}}{A nose for your robot.}{}
\card{blue}{CURVACE}{}{CURVACE}{Resource -- \textbf{Sensing}}{A vision sensor inspired by the the fly's ommatidia, designed by Floreano (EPFL).
}{}



\card{blue}{Sonar}{}{sonar}{Resource -- \textbf{Sensing}}{}{}
\card{blue}{Cheap IMU}{}{cheap_gyro}{Resource -- \textbf{Sensing}}{Uncalibrated accelerometer, gyrometer, and magnetometer.}{3.3 V; 9.90 USD}
\card{blue}{Bump Sensor}{}{bump_sensor}{Resource -- \textbf{Sensing}}{Works by measuring the capacitance of twelve electrode points. When an object comes close to the electrode connector, the measured capacitance changes.}{30 $\mu$A, 3.3V; 7 USD}


\clearpage
\card{blue}{Hokuyo Range-Finder}{}{hokuyo_urg}{Resource -- \textbf{Sensing}}{A reliable sensor. Maximum range is 8m.}{5 W; 2000 USD}
\card{blue}{Pressure Sensor}{}{pressure_sensor_PX302}{Resource -- \textbf{Sensing}}{A pressure to voltage transducer.}{235 USD}
\card{blue}{Thermal Imaging Camera}{}{thermal_imaging_camera}{Resource -- \textbf{Sensing}}{}{}



\card{blue}{Earth GPS Receiver}{}{earth_gps_receiver}{Resource -- \textbf{Sensing}}{Consumer grade, accurate to within a few meters (as long as the robot can see the satellites!)}{100 mA, 3.3 V; 25 USD}
\card{blue}{Compass}{}{compass}{Resource -- \textbf{Sensing}}{Detects the local magnetic field. Unpowered, requires vision system to read.}{0 W; 1 USD}
\card{blue}{Velodyne HDL-64E}{}{velodyne_HDL_64E}{Resource -- \textbf{Sensing}}{LIDAR, creates point cloud of distance data.\par\vfill\textit{With 2.2 million data points per second output rate, the HDL-64 provides all the distance sensing data you will ever need.}\par\vspace*{\fill}}{60 W; 29 lbs; 6000 USD}



\card{blue}{Linear Odometer}{}{linear_odometer}{Resource -- \textbf{Sensing}}{}{}
\card{blue}{1-point Range Finder}{}{1point_range_finder}{Resource -- \textbf{Sensing}}{}{}
\card{blue}{Camera}{}{camera}{Resource -- \textbf{Sensing}}{}{}


\clearpage
\card{blue}{Microphone}{}{microphone}{Resource -- \textbf{Sensing}}{}{250 $\mu$A, 5V; 10 USD}
\card{blue}{Photodiode}{}{photodiode}{Resource -- \textbf{Sensing}}{A photodiode is a semiconductor device that converts light into current. 
}{}
\card{blue}{Dynamic Vision Sensor}{}{dvs}{Resource -- \textbf{Sensing}}{}{}



\card{purple}{Rechargeable AA Battery}{}{aa_battery}{Resource -- \textbf{Power}}{A rechargeable Li-ion battery.}{30 g}
\card{purple}{Power Tether}{}{power_tether}{Resource -- \textbf{Power}}{A 1km long tether supplying as much power as you need (within reason).}{+$\infty$ W}
\card{purple}{1 Megawatt}{}{power}{Resource -- \textbf{Power}}{}{1 MW}



\card{purple}{100 Watt}{}{power}{Resource -- \textbf{Power}}{}{100 W}
\card{purple}{1 Milliwatt}{}{power}{Resource -- \textbf{Power}}{}{1 mw}
\card{purple}{The Power of the Sun}{}{the_power_of_the_sun}{Resource -- \textbf{Power}}{You can channel all the power irradiated by the sun into supporting your robotic system.
\par\vfill\textit{With great power comes great responsibility.}\par\vspace*{\fill}}{$3.828 \times {10}^{26}$ W}


\clearpage
\card{purple}{1 Watt}{}{power}{Resource -- \textbf{Power}}{}{1 W}
\card{brown}{Pebble}{}{pebble}{Resource -- \textbf{Memory}}{A uniquely identifiable landmark that can be placed anywhere and picked up again when that location is revisited.\par\vfill\textit{The rolling stone never gathereth mosse.}\par\vspace*{\fill}}{}
\card{brown}{640 KB}{}{640KB}{Resource -- \textbf{Memory}}{\textit{640K ought to be enough for anybody.}}{}



\card{brown}{Infinite Memory}{}{infinite_memory}{Resource -- \textbf{Memory}}{\textit{Always remember that you are absolutely unique. Just like everyone else.}}{}
\card{brown}{Ideal Stack}{}{stack}{Resource -- \textbf{Memory}}{No stack overflow!\par\vfill\textit{The Tower of Hanoi is composed of levels, decreasing in size, variable in number, that we have represented by eight disks of wood, pierced at their centers.}\par\vspace*{\fill}}{}
\card{brown}{One Bit}{}{1bit}{Resource -- \textbf{Memory}}{\textit{Memory, the warder of the brain.}}{}



\card{green}{Arduino Uno}{}{arduino_uno}{Resource -- \textbf{Computation}}{\textit{I have always loved to begin with the facts, to observe them, to walk in the light of experiment and demonstrate as much as possible, and to discuss the results.}}{20 USD}
\card{green}{Transistor}{}{1transistor}{Resource -- \textbf{Computation}}{A simple switch.\par\vfill\textit{The complexity for minimum component costs has increased at a rate of roughly a factor of two per year. Certainly over the short term this rate can be expected to continue, if not to increase.}\par\vspace*{\fill}}{}
\card{green}{NVidia Jetson TK1}{}{jetson_tk1}{Resource -- \textbf{Computation}}{\textit{Eep Opp Ork! Ah ah! Get in the capsule, baby.  We are blasting off.}}{199 USD}


\clearpage
\card{green}{Raspberry PI 2}{}{raspberry_pi_2}{Resource -- \textbf{Computation}}{\textit{I was working part time in a five-and-dime; My boss was Mr. McGee.}}{35 USD}
\card{green}{Infinite Computation}{}{infinite_computation}{Resource -- \textbf{Computation}}{You may instantly compute anything for which there is a known algorithm, on any machine.\par\vfill\textit{Infinite riches in a little room.}\par\vspace*{\fill}}{}
\card{green}{The Cloud}{}{cloud}{Resource -- \textbf{Computation}}{You have effectively infinite computation\ldots but not necessarily infinite bandwidth.\par\vfill\textit{``Somewhere, over the rainbow!''}\par\vspace*{\fill}}{}



\card{green}{FPGA}{}{fpga}{Resource -- \textbf{Computation}}{Field Programmable Gate Array\par\vfill\textit{Though wisdom wake, suspicion sleeps at wisdom's gate.}\par\vspace*{\fill}}{}
\card{green}{100-State DFA}{}{100dfa}{Resource -- \textbf{Computation}}{States and state transition function are user-defined.\par\vfill\textit{We must accept finite disappointment, but never lose infinite hope.}\par\vspace*{\fill}}{}
\card{green}{TrueNorth Processor}{}{truenorth}{Resource -- \textbf{Computation}}{The neuromorphic processor created by IBM.
\par\vfill\textit{No one ever got fired for buying IBM.}\par\vspace*{\fill}}{}



\card{green}{Macbook Pro}{}{macbook_pro}{Resource -- \textbf{Computation}}{Includes all default software and hardware.\par\vfill\textit{Most people have no concept of how an automatic transmission works, yet they know how to drive a car. \ldots{} You don't have to understand any of this stuff to use Macintosh.}\par\vspace*{\fill}}{}
\card{green}{Oracle}{}{oracle}{Resource -- \textbf{Computation}}{Answers a single one-bit question of your choice per second.\par\vfill\textit{I am Sir Oracle, And when I ope my lips, let no dog bark!}\par\vspace*{\fill}}{}
\card{blue}{Smoke Signals}{}{smoke_signal}{Resource -- \textbf{Communication}}{\textit{There is no fire without some smoke.}}{}


\clearpage
\card{blue}{Communication Tether}{}{comm_tether}{Resource -- \textbf{Communication}}{A cable, with gigabit ethernet capacity, connected to a base station.\par\vfill\textit{Nae man can tether time or tide.}\par\vspace*{\fill}}{}
\card{blue}{WiFi}{}{wifi_802_11}{Resource -- \textbf{Communication}}{A network card compatible with the IEEE 802.11ad standard.\par\vfill\textit{I sincerely doubt that the guy who sells socks by the overpass is providing high-speed Internet to the community.}\par\vspace*{\fill}}{}
\card{blue}{Carrier Pigeon}{}{carrier_pigeon}{Resource -- \textbf{Communication}}{Avian communication channel as specified by RFC 1149.\par\vfill\textit{Every time I feel alone; And slightly blue; That's when I begin to think; It's what I'd like to start to do.}\par\vspace*{\fill}}{}



\card{blue}{Acoustic Modem}{}{acoustic_modem}{Resource -- \textbf{Communication}}{This gives you 10 bit/s on a good day.\par\vfill\textit{I'm not asking much. \ldots What I want from you is your voice.}\par\vspace*{\fill}}{}
\card{blue}{The Ansible}{}{ansible}{Resource -- \textbf{Communication}}{Provides infinite bandwidth at zero latency.\par\vfill\textit{You remember the ansible, the machine I showed you in the ship, which can speak instantly to other worlds, with no loss of years---it was that that they were after, I expect.}\par\vspace*{\fill}}{}
\card{blue}{Weak Ansible}{}{weak_ansible}{Resource -- \textbf{Communication}}{A channel with infinite bandwidth, zero power consumption, but a 1 minute latency.}{}



\card{white}{The Goal Posts Have Moved}{}{goal_posts}{Special}{You can change the current goal by changing either the \emph{Task} or the \emph{Environment} card.
\par\vfill\textit{``We must run as fast as we can, just to stay in place. And if you wish to go anywhere you must run twice as fast as that.''
}\par\vspace*{\fill}}{}
\card{white}{Theory of Everything}{}{everything16}{Special}{A reviewer can use this card to dismiss the paper as over-reaching.
\par\vfill\textit{The results should be more concrete.}\par\vspace*{\fill}}{}
\card{white}{The Power of Friendship}{}{the_power_of_friendship}{Special}{Use a card belonging to somebody else.}{}


\clearpage
\card{white}{Competitive Collaboration}{}{competitive_collaborations}{Special}{You can use the cards of another player to create a design. However, if the paper is accepted, only one of you,  decided randomly, will get the \emph{Name Recognition} reward.
}{}
\card{white}{2$\times$ Multiplier}{}{mult2}{Special}{One resource can be multiplied by~2.}{}
\card{white}{5$\times$ Multiplier}{}{mult5}{Special}{One resource can be multiplied by~5.}{}



\card{white}{10$\times$ Multiplier}{}{mult10}{Special}{One resource can be multiplied by~10.}{}
\card{white}{A Russian Did It in the 1960s}{}{russian}{Special}{The paper under review is rejected.
}{}
\card{white}{Fundamental Theorem}{}{fundamental01}{Special}{This card can be played by a reviewer to reject a paper by appealing to authority.
\par\vfill\textit{The Fundamental Theorem of Robotics (Egerstedt, 2002) subsumes all subsequent results.}\par\vspace*{\fill}}{}



\card{white}{I Have an Idea!}{}{do_research}{Special}{Create a new card using one of the empty cards. Put it randomly in the deck.
}{}
\card{white}{3D Printer}{}{3dprinter}{Special}{\textit{Everything is now possible!}}{}
\card{white}{$\infty$ Multiplier}{}{multinf}{Special}{One resource can be multiplied by~$\infty$.}{}


\clearpage
\card{violet}{Very Dedicated Grad Student}{}{dedicated_grad_student}{Resource -- \textbf{Collaborator}}{Genius is one percent inspiration, ninety nine percent perspiration.
}{}
\card{violet}{Steve LaValle}{}{lavalle}{Resource -- \textbf{Collaborator}}{Thanks to an optimal design of the minimal filter and policy, you can \emph{handwave away} all the concerns regarding the computation requirements of the proposed solution.
\par\vfill\textit{I was never a big fan of patents, but now I have a couple.}\par\vspace*{\fill}}{}
\card{violet}{Friend on IRB Committee}{}{irb_approval}{Resource -- \textbf{Collaborator}}{The IRB will approve your project in spite of its questionable ethics. This card is especially useful in conjuction with \textit{Very Dedicated Grad Student}.
}{}



\card{violet}{Lazy Graduate Student}{}{lazy_graduate_student}{Resource -- \textbf{Collaborator}}{\textit{Procrastination is not the same thing as laziness. Laziness is when you don't want to do anything. Procrastination is when you don't want to do the one thing you really ought to be doing.}}{}
\card{magenta}{Play as a Goalie}{}{soccer}{Task}{Play as a goalie in the World Cup.
}{}
\card{magenta}{Find All Easter Eggs}{}{find_easter_eggs}{Task}{}{}



\card{magenta}{Assemble IKEA Furniture}{}{assemble_ikea}{Task}{}{}
\card{magenta}{Perform Surgery}{}{surgery}{Task}{}{}
\card{magenta}{Sort Fruits by Color}{}{sort_fruits}{Task}{}{}


\clearpage
\card{magenta}{Rescue All Survivors}{}{rescue_survivors}{Task}{}{}
\card{magenta}{Change a Diaper}{}{diaper}{Task}{}{}
\card{magenta}{Play Chess}{}{chess}{Task}{}{}



\card{magenta}{Find and Disarm an IED}{}{IED_disposal}{Task}{}{}
\card{magenta}{Intel Lab, Seattle}{}{intel_lab}{Environment}{}{}
\card{magenta}{Under the Sea}{}{underwater}{Environment}{}{}



\card{magenta}{Pacman's Maze}{}{pacman_maze}{Environment}{\textit{If Pac-Man had affected us as kids, we'd all be running around in dark rooms, munching pills and listening to repetitive electronic music.}}{}
\card{magenta}{Lake Michigan}{}{lake_michigan}{Environment}{Did you remember the O-rings?}{}
\card{magenta}{Mount Etna, Sicily}{}{etna}{Environment}{}{}


\clearpage
\card{magenta}{Deep Space}{}{deep_space}{Environment}{}{}
\card{magenta}{The Bat Cave}{}{batcave}{Environment}{}{}
\card{magenta}{Victoria Crater, Mars}{}{mars}{Environment}{Mars is the only planet completely inhabited by robots.
}{}



\card{magenta}{Echo Base, Hoth}{}{hoth}{Environment}{}{}
\card{magenta}{The Dagobah Swamps}{}{dagobah}{Environment}{\textit{I met him in a swamp down in Dagobah, where it bubbles all the time like a giant carbonated soda.}}{}
\card{magenta}{The Forest Moon of Endor}{}{endor}{Environment}{}{}



\card{magenta}{The Bates Motel}{}{bates_motel}{Environment}{}{}
\card{magenta}{Tatooine}{}{tatooine}{Environment}{}{}
\card{magenta}{Ice Rink}{}{ice_rink}{Environment}{}{}


\clearpage
\card{magenta}{Ski Slope}{}{ski_slope}{Environment}{}{}
\card{indigo}{Name Recognition}{}{name_recognition}{Rewards}{This card counts as one positive reviewer.
}{}
\card{indigo}{Name Recognition}{}{name_recognition2}{Rewards}{This card counts as one positive reviewer.
}{}



\card{indigo}{Bitterness}{}{bitterness}{Rewards}{Your negative opinion as a reviewer counts double.
}{}
\card{indigo}{Bitterness}{}{bitterness2}{Rewards}{Your negative opinion as a reviewer counts double.
}{}
\card{white}{}{}{research_card}{}{}{}



\end{document}
